Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
clarify some sentences - remove statement about version control systems, as this didn't add to the relevant discussion

The papers submitted to this panel, and several others, include lots of general
recommendations for processes, practices, tools, etc. One of the papers
suggested that a ``Software Sustainability Institute'' should be vested with
the authority to develop standardized quality processes, a central common
repository, central resources for services and consulting, a think tank of
sorts, and a software orphanage center. The idea received some resistance,
stating difficulties in acting as a central common repository with so many
compelling alternatives, and as an orphanage. The point for centralization of
communication/point of contact might be reasonable, with the statement that
``vested with authority'' is perhaps too strong, but ``providing tools if
needed'' might be more appropriate. The wider open source community is moving
to a model of distributed version control (Git, Mercurial, Bazaar, etc), rather
than more centralized, as discussed in the second keynote.

>>>>

The papers submitted to this panel, and several others, include lots of general
recommendations for processes, practices, tools, etc. One of the papers
suggested that a ``Software Sustainability Institute'' should be vested with
the authority to develop standardized quality processes, a central common
repository, central resources for services and consulting, a think tank of
sorts, and a software orphanage center. The idea of one common repository received
some resistance, with so many compelling alternatives available, e.g. BitBucket or
GitHub. The point for centralization of communication/point of contact was seen as
reasonable, with the statement that ``vested with authority'' is perhaps too strong,
but ``providing tools if needed'' might be more appropriate.
